\documentclass[11pt]{article}

% ---------- Fonts ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ebgaramond}
\renewcommand{\familydefault}{\rmdefault}

% ---------- Page Layout ----------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black]{hyperref}
\usepackage{ragged2e}
\usepackage{xcolor}

\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt,leftmargin=1.2em}
\renewcommand\labelitemi{$\vcenter{\hbox{\large\textbullet}}$}

% ---------- Section Formatting ----------
\titleformat{\section}{\Large\bfseries}{}{0pt}{\MakeUppercase}
\titlespacing*{\section}{0pt}{8pt plus 2pt}{4pt}

% ---------- Custom Macros ----------
\newcommand{\divider}{\vspace{6pt}\hrule height 0.4pt \vspace{6pt}}
\newcommand{\name}[1]{{\Huge\bfseries #1}}
\newcommand{\contact}[1]{\normalsize #1}
\newcommand{\rolelocdates}[3]{\textbf{#1} \hfill #3\\\textit{#2}}

% ---------- Document ----------
\begin{document}
	\RaggedRight
	
	% ===== Header =====
	\name{Daud Khalid}\par
	\contact{\href{mailto:mail@daudkhalid.ca}{mail@daudkhalid.ca} \,|\, Oakville, ON \,|\, \href{https://daudkhalid.ca}{daudkhalid.ca}}
	\divider
	
	% ===== SUMMARY =====
	\section{Summary}
	Aspiring Software Engineer with hands-on experience developing full-stack and command-line applications. Strong foundation in data structures, algorithms, and software design principles. Experienced in collaborative environments and technical support roles, with proven communication and problem-solving skills.
	
	% ===== TECHNICAL SKILLS =====
	\section{Technical Skills}
	\begin{itemize}
		\item \textbf{Languages:} Python, C, Java, JavaScript, TypeScript, SQL
		\item \textbf{Frameworks \& Tools:} React, Node.js, Supabase, Git, Linux, Bash
		\item \textbf{Concepts:} Data Structures, Algorithms, Object-Oriented Design, Database Management, Networking
		\item \textbf{Other:} Azure AD (Entra ID), Active Directory, user provisioning, software troubleshooting
	\end{itemize}
	
	% ===== PROJECTS =====
	\section{Projects}
	
	\textbf{JellyCLI} – \textit{TUI for Jellyfin Media Server} \hfill \href{https://github.com/daudk3/JellyCLI}{github.com/daudk3/JellyCLI}\\
	\begin{itemize}
		\item Developed a terminal-based user interface to interact with Jellyfin’s media APIs.
		\item Implemented browsing, playback, and search functionality with responsive TUI design.
		\item Utilized Python and rich CLI libraries to streamline user navigation and server control.
	\end{itemize}
	
	\textbf{Flight Management System} – \textit{Full-Stack Web App} \hfill \href{https://github.com/daudk3/flight-management-system}{github.com/daudk3/flight-management-system}\\
	\begin{itemize}
		\item Built a flight scheduling and booking system using React and Supabase.
		\item Designed relational data models and integrated authentication and CRUD operations.
		\item Deployed front-end and backend services with modular components and reusable APIs.
	\end{itemize}
	
	% ===== WORK EXPERIENCE =====
	\section{Work Experience}
	
	\rolelocdates{Wilfrid Laurier Univeristy Service Desk}{Student Service Desk Analyst}{2025 -- Present}
	\begin{itemize}
		\item Provided cross-platform technical support across Windows, macOS, and mobile environments.
		\item Assisted users with Azure AD authentication, MFA setup, and account provisioning.
		\item Collaborated with system administrators to resolve synchronization and access issues.
		\item Developed strong troubleshooting, communication, and documentation skills in a fast-paced academic IT setting.
	\end{itemize}
	
	\rolelocdates{Walmart Canada}{Customer Fulfillment Associate}{2022}
	\begin{itemize}
		\item Delivered accurate, time-sensitive order fulfillment and coordinated with team members to ensure efficiency.
		\item Mentored new associates to uphold process consistency and operational quality.
	\end{itemize}
	
	% ===== EDUCATION =====
	\section{Education}
	\textbf{Wilfrid Laurier University} \hfill 2021 -- 2027\\
	Honours Bachelor of Science in Computer Science (In Progress)\\
\end{document}